---
output: 
    revealjs::revealjs_presentation:
      theme: solarized
      highlight: pygments
      transition: fade
---

```{r echo=FALSE, message=TRUE, warning=FALSE}
library(ggplot2)
library(knitr)
library(kableExtra)



# Switch off showing code...
knitr::opts_chunk$set(echo=FALSE)

# Function to to column of data where each entry can have 
# more than one piece of text separated by a comma
# and return a vector with all the terms
collectTerms <- function(entries){
  unlist(strsplit(entries,"[,]")) -> r
  
  # Strings may have a leading space which we'll remove
  roles <- sapply(r,function(s){
    l <- unlist(strsplit(s,"^ "))
    if ( length(l) == 1 ){
      return(l)
    }
    else{
      return(l[length(l)])
    }
  })
  return(as.vector(roles))
}


# Function to remove blank entries from a column
# and then print them out nicely
printComments <- function(entries,label=NULL){
  r <- sapply(entries,function(e){
    if ( e == ""){
      NULL
    }
    else { e }
 })
  text_tbl <- data.frame(x=as.vector(unlist(r)))
  names(text_tbl) <- label
                        
  kable(text_tbl) %>%
  kable_styling(full_width = F) %>%
  column_spec(1, width = "30em",background="khaki")
#  kable(as.vector(unlist(r)),label=label)
}

# Convert columns of data on individual themes and recast it
# as a single vector
turnIntoOneColumn <- function(data,cols){
  colNames <- names(data)[cols]
  nRows <- dim(data)[1]
  labels <- rep(colNames,each=nRows)
  results <- c()
  for ( label in colNames ){
    results <- c(results,data[,label])
  }
  return(data.frame(theme=labels,score=results))
}

# Remove rows where the theme scores have zero variance
removeZeroVarRows <- function(data,cols){
  nRows <- dim(data)[1]
  keep <- c()
  for ( i in 1:nRows ){
    if (var(as.numeric(data[i,cols])) > 1e-6){
      keep <- c(keep,i)
    }
  }
  return(data[keep,])
}

survey <- read.csv("Questionnaire.csv",stringsAsFactors=FALSE)
```

<br>
<br>
<br>
<br>
<br>
<p align="left"> Results of survey </p>
<br>
<br> 
<p align="right">  Details can be found at https://github.com/hughshanahan/FAIRTerminologySurveyAnalysis </p>
----

<br>
<br>
<br>
<br>
<p align="left"> 
 16 Responses
</p>

<br>
<br>
<p align="left"> 
 Demographics indicate feedback from a wide spread of roles and domains. 
</p>

<!-- ## **A small number are representing their organisation's opinions** -->

<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- ggplot(data=survey,aes(x=Organisation)) + geom_bar() + scale_y_continuous(breaks=c(2,4,6,8,10)) -->
<!-- ``` -->

<!-- ## **There is a wide spread of roles** -->

<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- x <- data.frame(roles=collectTerms(survey$Role)) -->
<!-- ggplot(data=x,aes(x=roles)) + geom_histogram(stat="count") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) -->
<!-- ``` -->
<!-- ---- -->

<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- printComments(survey$OtherRoles,"Other possible role descriptions") -->
<!-- ``` -->

<!-- ---- -->
<!-- **There is a wide spread of domains** -->

<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- x <- data.frame(ResearchDomains=collectTerms(survey$ResearchDomain)) -->
<!-- ggplot(data=x,aes(x=ResearchDomains)) + geom_histogram(stat="count") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) -->
<!-- ``` -->
<!-- ---- -->
<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- printComments(survey$OtherResearchDomain,"Other research domains") -->
<!-- ``` -->

----
<p align="left"> Use case - Search for course materials </p>

<br>
<br>
<br>

* Select terms from terminology.

* Courses previously labelled using the terminology on site such as TESS.

* Courses selected on the basis of the terms selected. 

----


General agreement that Search for Course Materials is a valid use case.

```{r echo=FALSE, message=TRUE, warning=FALSE}
ggplot(data=survey,aes(x=CourseMaterialsSearch)) + geom_bar() + scale_y_continuous(breaks=c(4,8,12,16,20)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

----

```{r echo=FALSE, message=TRUE, warning=FALSE}
printComments(survey$CourseMaterialsSearchReasonNo,"Negative comments aren't negative!")
```

----
<p align="left"> Curriculum design </p>

<br>
<br>
<br>

* Upload course descriptions and do word match to find terms. 

* Select courses to maximise coverage or coherent coverage (all of a major topic etc.)

----


General agreement that Curriculum design is a valid use case.

```{r echo=FALSE, message=TRUE, warning=FALSE}
ggplot(data=survey,aes(x=CurriculumDesign)) + geom_bar() + scale_y_continuous(breaks=c(4,8,12,16,20)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


----
```{r echo=FALSE, message=TRUE, warning=FALSE}
printComments(survey$CurriculumDesignReasonsNo,"Though more scepticism here")
```

----



But much less support for the other cases

```{r echo=FALSE, message=TRUE, warning=FALSE}
ggplot(data=survey,aes(x=FAIRJobAssessment)) + geom_bar() + scale_y_continuous(breaks=c(4,8,12,16,20)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

----



```{r echo=FALSE, message=TRUE, warning=FALSE}
ggplot(data=survey,aes(x=ArticleQualityControl)) + geom_bar() + scale_y_continuous(breaks=c(4,8,12,16,20)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

----



```{r echo=FALSE, message=TRUE, warning=FALSE}
ggplot(data=survey,aes(x=DataRepositoryUploaderSkillsCheck)) + geom_bar() + scale_y_continuous(breaks=c(4,8,12,16,20)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

----


<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- printComments(survey$ReasonsNo,"Reasons why this isn't a valid use case") -->
<!-- ``` -->

<!-- ---- -->
Many interesting suggestions for other use cases - but no real consensus there (perhaps for software FAIR but...) 

<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- printComments(survey$OtherUseCases,"Other possible use case") -->
<!-- ``` -->

----


Use cases that would be used reflects the above

```{r echo=FALSE, message=TRUE, warning=FALSE}
x <- data.frame(UseCasesEmployed=collectTerms(survey$UseCasesWouldEmploy))
ggplot(data=x,aes(x=UseCasesEmployed)) + geom_histogram(stat="count") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

----



**Thesaurus is favoured**

```{r echo=FALSE, message=TRUE, warning=FALSE}
ggplot(data=survey,aes(x=TerminologySelection)) + geom_histogram(stat="count") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

----


```{r echo=FALSE, message=TRUE, warning=FALSE}
#printComments(survey$ExplanationTerminologySection)
printComments(survey[which(survey$TerminologySelection=="Controlled Vocabulary"),"ExplanationTerminologySection"],"Reasons for choosing Controlled Vocabulary")
```

----


```{r echo=FALSE, message=TRUE, warning=FALSE}
printComments(survey[which(survey$TerminologySelection=="Ontology"),"ExplanationTerminologySection"],"Reasons for choosing Ontology")
```

----


```{r echo=FALSE, message=TRUE, warning=FALSE}
printComments(survey[which(survey$TerminologySelection=="Thesaurus"),"ExplanationTerminologySection"],"Reasons for choosing Thesearus")
```


----



Overall people seem okay with the top concepts
```{r echo=FALSE, message=TRUE, warning=FALSE}
scoreData <- turnIntoOneColumn(survey,c(21:29))
ggplot(data=scoreData,aes(x=theme,y=score)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_y_continuous(breaks=c(1:10))
```


----
  


<!-- ```{r echo=FALSE, message=TRUE, warning=FALSE} -->
<!-- printComments(survey$OtherTopLevelConcepts,"Other possible top level concepts") -->
<!-- ``` -->

